Example case study in GMSE

### 2018-08-17 notebook/ms/SI3.Rmd
Add half of the response to Reviewer 1 minor comment 4. Also consider simply adding a new SI (probably not best because this will require yet more things to link to, possibly generating confusion)

Table 1: Select parameter values for initialising generalised management strategy evaluation simulations

@@

>>>>

Table 1: Select parameter values for initialising generalised management strategy evaluation simulations. See [below](#nondefaults) for explanation of non-default values.

@@

Non-default options in default GMSE sub-models {#nondefault}
--------------------------------------------------------------------------------

Within the default submodels of GMSE, there are several non-default options that can be set using arguments to `gmse` and `gmse_apply`. Brief explanations of these non-default options appear in the [GMSE documentation](https://cran.r-project.org/web/packages/GMSE/GMSE.pdf) (also [listed](https://confoobio.github.io/gmse/reference/gmse.html) on the [GMSE website](https://confoobio.github.io/gmse/)). Here we further explain some of the less obvious or less intuitive options available in GMSE v0.4.0.6, for which additional explanation beyond the GMSE documentation may be warranted. Future versions of GMSE are expected to expand upon these options.

**res_move_type**: Resources in default GMSE v0.4.0.7 sub-models can move in one of three ways. These different movement types are listed below, and are taken as arguments to `gmse` (e.g., `gmse(res_move_type = 2)`).

  0. *No movement*. Given this option, resources do not move at all in the default resource sub-model, and instead remain on the location at which they are initialised.
  1. *Uniform movement in any direction up to `res_movement` cells away from a resource's original location* (default). In uniform movement, the resource moves to a new cell within some distance `res_movement` of its original location in each time step. Distance therefore includes diagonal movement, such that a resource capable of moving `res_movement = 1` cell away can go to any of the eight adjacent cells around its current location; it can also remain on its current cell. Similarly, a resource capable of moving `res_movement = 2` cells away can go to any of the 24 cells surrounding its current location, or remain on its current cell. The distance (in cells) moved in the x-direction (i.e., left to right) and y-direction (i.e., up and down), is sampled from a uniform distribution, meaning that all reachable cells (including the resource's current cell) have equal probability of being selected as the resource's new cell location.
  2. *Poisson selected movement distance and direction*. In this movement type, the distance (in cells) moved in the x-direction and the y-direction are sampled from a Poisson distribution using `res_movement` as the rate parameter (i.e., the mean movement distance in each direction). Using this movement type is not generally recommended because it is not likely to be biologically realistic (e.g., diagonal movement is rare because selection of both high x-direction and high y-direction values is unlikely).
  3. *Uniform movement in any direction up to `res_movement` cells away from a resource's original location `res_movement` times.* Like option (1), when moving, resources can travel in any direction up to `res_movement` cells from their current location with equal probability. What is different about this option is that uniform movement in any direction is occurs $C =$ Poisson(`res_movement`) times. In other words, when a resource moves, it first decides how many different cells it will visit ($C$), as determined by sampling from a Poisson distribution with a rate parameter of `res_movement` (i.e., the mean number of visited cells will be `res_movement`). Upon leaving a cell, the resource will move in the same way as defined in option (1) above, by choosing a cell within `res_movement` distance (in cells) of its current cell. It continues moving in this way until $C$ cells have been visited. This type of movement has been used in some individual-based models of plant-pollinator interactions [e.g., @Duthie2013; @Wilson2003].

**res_death_type**: Resources can be removed from the model in one of three ways within the default resource sub-model, thereby simulating resource death. It is important to note that `res_death_type` refers only to removal that occurs within the resource sub-model; removal from user actions (e.g., death from shooting) occurs within the user sub-model.

  1. *Density-independent removal*. Given this option, there is no density-dependent removal of resources within the resource sub-model. Resources are simply removed with a probability of `removal_pr` each time the submodel is run. This option should be used with great care because in the absence of density-dependence, it is possible for the population of resources to increase without limit and thereby greatly slow down simulation times. 
  2. *Density-dependent removal*. Given this option, removal of resources within the resource sub-model is caused entirely by density effects. The probability that a resource is removed is a function of the resource carrying capacity set using the `res_death_K` parameter. If the number of resources ($N$) is greater than `res_death_K` ($K$), then the probability that an individual resource is removed is defined by $(N - K) / N$. Removal then occurs independently for each resource based on this probability.
  3. *Density-independent and density-dependent removal*. This option allows a combination of both options (1) and (2), which affect removal independently. In other words, each resource is assigned a probability of removal `removal_pr` as in (1), and then independently assigned another probability of removal based on `res_death_K` as in (2). If removal occurs as a consequence of (1), (2), or both, then the resource is removed.

**observe_type**: Observation of resources in the observation model can occur in one of four ways.

**obs_move_type**:
